\ttitle

### 2013-10-28 Chapters/Chapter4.tex
WIP: Chapter 4

%----------------------------------------------------------------------------------------
\section{Outline}
\begin{itemize}
  \item Based on the problem statement with current research as stated in Chapter \ref{Chapter3}
  \item Adjust method to needs
  \item Explain using graphs, pseudo-algorithms. Make clear distinction in origin of ideas and why to apply
\end{itemize}

>>>>

%----------------------------------------------------------------------------------------
\section{Outline}
\emph{Not intented for the reader.}
\begin{itemize}
  \item Based on the problem statement with current research as stated in Chapter \ref{Chapter3}
  \item Adjust method to needs
  \item Explain using graphs, pseudo-algorithms. Make clear distinction in origin of ideas and why to apply
\end{itemize}

\subsection{Experiment notes}
\begin{itemize}
  \item ICSS/CUSUM is goed in het vinden van variance changes. Niet goed in mean veranderingen.
  \item Problemen met SVM methode: ook na de verandering blijft de threshold nog stijgen;
  \item geprobeerd direct model-reset te doen na change point, maar dan kan je achteraf niet meer verder analyseren.
  \item Veranderingen in mean geven ``extra'' change point wanneer alle data weer in het window zit. Zie \ref{fig:jumping_mean_ratios} op de 50-tallen.
\end{itemize}

\begin{description}
  \item[Data gathering] Explain data gathering methods. Refer to chapter 5 and 6 for articifial and real-world details.
  \item[Model construction] Explain SVDD model construction and updating.
  \item[Model properties] Explain the SVDD properties that are used to calculate the change indication.
  \item[Change detection] Explain the interpretation of the properties, the possible (modulair) methods to give change indication
\end{description}

\TODO{Write chapter introduction/outline. Give overview of method approach and refer to each section for details of that stage.}

\input{./Chapters/Chapter4/data_gathering}
\input{./Chapters/Chapter4/model_construction}
\input{./Chapters/Chapter4/model_properties}
\input{./Chapters/Chapter4/change_detection}

 --- OLD ---
\input{./Chapters/Chapter4/change_indication}
\input{./Chapters/Chapter4/overview}
\input{./Chapters/Chapter4/algorithms}

### 2013-10-28 Chapters/Chapter5/artificial_data.tex
WIP: Chapter 4

>>>>

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/notes/jumping_mean_camci.eps}
  \caption[Jumping mean camci]{Jumping mean camci}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/notes/jumping_mean_camci_thresholds.eps}
  \caption[Jumping mean camci thresholds]{Jumping mean camci, thresholds}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/notes/jumping_mean_camci_ratios_10.eps}
  \caption[Jumping mean camci ratios]{Jumping mean camci ratios, last 10}
  \label{fig:jumping_mean_ratios}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/notes/jumping_variance.eps}
  \caption[Jumping variance]{Jumping variance}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/notes/jumping_variance_thresholds.eps}
  \caption[Jumping variance thresholds]{Jumping variance, thresholds}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/notes/jumping_variance_ratios_10.eps}
  \caption[Jumping variance ratios]{Jumping variance ratios, last 10}
\end{figure}
